---
title: "Performance Evaluation Of Terapixel Rendering in Cloud(Super) Computing Project"
author: "Cahyadi/200511881"
date: "1/23/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(fig.align = "center")
```

# CSC8634 Project: Performance Evaluation of TeraPixel Rendering in Cloud (Super) Computer


## Introduction
&nbsp;&nbsp;&nbsp;Cloud technology, a relatively new technology that is based on utilising the internet infrastructure to the fullest has seen a major increase in popularity in recent years. This success could be attributed to the huge growth of the Tech Industries that seen many new Unicorns; a term first mentioned by Aileen Lee on 2013, used to describe privately owned start-up companies that valued more than 1 billion USD. One of many reasons why the emergence of these "Unicorns" of Tech world brought popularity to Cloud technologies is that Cloud technologies provide a huge benefit to a start-up companies to further expanse and scale their business with greater flexibility and relatively minimum cost and commitment. Start-up companies now have the option to rent  

```{r include = FALSE}
library(ProjectTemplate)
load.project()

# Source the code from analysis script in src folder
source("src/analysis1.R")

```

## Data understanding

The oiginal Data

```{r , echo=FALSE}

```

```{r, echo= FALSE}

g2 = ggpairs(totalRenderData[,c(7,10:12)], title = "Total Render Plot")
print(g2)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
